State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication

### 2021-11-11 prism-backend/research/soa_review/ac.tex
Review of FHS19.

@@

@@

\cite{sms+19} seems to be the most efficient one (note: relies on the
Fiat-Shamir heuristic). Credentials are only composed by two G1 elements,
independently on the number of attributes.

@@

\begin{itemize}
\item \cite{bcc+09}: Delegation.
\item \cite{fhs19}: Structure-preserving signatures for AC.
\item \cite{aks12}: ACs with revocation.
\end{itemize}

@@

>>>>

\item[\cite{fhs19}:] Based on Structure Preserving Signatures from equivalence
  classes (SPS-EQ). The approach resembles that of \cite{ckl+15} in that it
  uses a structure preserving primitive, and signs (commitments of) sets of
  messages. However, they aim to avoid (as they claim) costly zero-knowledge
  proofs. Basically, upon setup, a set commitment scheme is set up. Each user
  generates a keypair. To obtain a credential on a set of attributes $A$, the
  user proves knowledge of the user secret key, which is used as randomness
  for a set commitment over $A$. The issuer (proves knowledge of the secret
  key and) returns a SPS-EQ signature over $A$. To show the credential, the
  user randomizes the commitment set and the signature, reveals the required
  subset $D$ of $A$, and computes a witness that indeed $D \subset A$, as well
  as a proof knowledge of the randomness used to randomize the credential (to
  prevent replays). 

@@

\item[\cite{fhs19}:] Gives a game-based security model, with anonymity and
  unforgeability being the main security properties (besides correctness).
  Unforgeability resembles the traceability property of group signatures,
  which are recognised as an influence in their modelling -- more specifically,
  \cite{bmw03} (the model -- and the oracles therein -- definitely resembles
  the BMW model for GSs). The authors claim to be the firsts to give a well defined and
  formal model for ACs, besides \cite{ckl+15} (which gives game-based properties
  in the simulation paradigm) and \cite{cdhk15} (which follows the UC framework).
  However, \cite{fhs19} claims that adopting non-simulation based definitions
  allows them to reach a more efficient construction. They also support malicious
  issuer key generation, as issuers have to prove knowledge of their secret keys
  (which allows extraction in the games).
  An interesting aspect of their model is that all attributes in their
  credentials are learned by the issuer -- i.e., there are no blindly signed
  attributes. This implies that it is not possible to sign secret keys owned
  by the users (as in the conventional CL credentials). Then, for showing a
  credential, all the user has to do is reveal the attributes s/he is required
  to show. This has the disadvantage that, depending on the use case, this may
  be trivial to attack. For instance, assume a COVID-like pandemic situation,
  in which citizens have to prove being vaccinated. An AC system for this use
  could be naively defined as: { Type of vaccine, Date of vaccination }. But
  this is very susceptible to dictionary attacks, and leaves much to the
  engineering/implementation level. E.g., if it is easy for an eavesdroper
  to get hold of a credential (not even the plaintext attributes), s/he can
  just iterate through the small list of possible values, and then take
  advantage of the ``stolen'' credential. This is certainly secure under the
  model defined in \cite{fhs19}, but it is definitely easy for implementations
  following this model to go wrong...
  They also model only interactive show processes. Furthermore, to prevent
  replay attacks, the user has to prove knowledge of some randomness included
  in the credential. However (\textbf{cross-check this!}), since signatures
  are randomizable without knowledge of any secret value, any adversary that
  learns a credential (not necessarily any plaintext attribute associated to
  it), would be capable of authenticating through a dictionary attack in case
  of small attribute ranges.
  Note: this may just be a modelling issue (or not even that, cross-check later
  in case I misunderstood something). In their construction, they include
  a secret key of the user in the credentials, of which the user has to prove
  knowledge during the issue protocol. They do this by ``reusing'' the user
  secret key as the randomness employed for the set commitment scheme, and
  requiring the user to prove knowledge of the corresponding public key.
  However, I am not sure of whether or not this somehow thwarts the previously
  mentioned ``attack'', which affects the show protocol (\todo{i.e., the user does
    not need to prove knowledge of the usk during show, no?} \note{Actually, it
    should not, as it would probably prevent anonymity}) In any case, even if
  the specific construction and instantiation thwarts this attack, I think their
  model allows it.

@@

\cite{sms+19} seems to be the most efficient one (note: relies on the
Fiat-Shamir heuristic). Credentials are only composed by two G1 elements,
independently on the number of attributes. \todo{Cross-check this after
  review.}

\cite{cdhk15} and \cite{fhs19} achieve credential showings of size independent
of the number of attributes.

@@

\begin{itemize}
\item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
\item \cite{aks12}: ACs with revocation.
\item \cite{asm06}: This seems to be the origin of the BBS+ branch of ACs (also,
  probably \cite{aks12} is in this family).
\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
  such as ECDSA) signatures.
\item \cite{cl11}: ACs from aggregate signatures.
\end{itemize}

@@

Concepts in ACs: multishow, one-show (Brands et al); interactive vs non-interactive
showings (differentiation made in \cite[p.6]{fhs19} but, why would one want interactive,
in the real world?)

Which schemes support comibning credentials from multiple issuers? I think this
is directly obtained in the schemes following the CL approach; but others?

A recurrent claim in schemes avoiding using zero-knowledge proofs of knowledge
of some attributes being included in a credential is that these proofs are costly
(like, linear in the number of attributes). Yet, they resort to other primitives
that may also be costly (e.g., predicate encryption \cite{dmm+18}) or somehow move
the cost to some other place (e.g., \cite{fhs19} uses a vector commitment scheme
that requires a public key with size that grows with the number of attributes
that \emph{can} be committed). It would be nice to have a detailed and complete
(e.g., not skipping the data that makes one scheme look bad, like the size of
the public keys) comparison. And, ideally, with concrete instantiations (not only
theoretical analysis)?
